---
title: "Introduction to StatComp21095"
author: "Liu Dingding"
date: "2021/12/17"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp21095}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp21095__ is a simple R package containing two functions related to sampling method and a parameter estimation method called LDPE for the 'Statistical Computing' course. In the first method,two functions are considered, namely, _bootunif.sample_ (generate random nubers ) , _bootunif_ (compute statistics like bootstrap statistics using _bootunif.sample_), _fh.hat_(kernel density estimation using Gauss distribution) and _CVh_(choose optinal bandwith given an initial of bandwiths). In addition to them, _gibbs_C_ using C++ for homework is given.


## _bootunif.sample_ and _bootunif_

The source R code for _bootunif.sample_ is as follows:
```{r}
bootunif.sample<-function(x){
  if(!is.numeric(x))
    stop("data must be a numeric vector!\n")
  if(!(is.atomic(x)||is.list(x)))
    stop("data must be a numeric vector!\n")
  n<-length(x)
  x0<-sort(x)
  data<-sapply(1:(n-1), function(i){
    runif(1,x0[i],x0[i+1])
  })
  data1<-c(x0[1],data,x0[n])
  return(data1)
}
```


The source R code for _bootunif_ is as follows:
```{r}
bootunif<-function(data,statistic,R){
  if(!is.numeric(data))
    stop("data must be a numeric vector!\n")
  if(!(is.atomic(data)||is.list(data)))
    stop("data must be a numeric vector!\n")
  data0<-replicate(R,expr = {
    list(bootunif.sample(data))
  })
  res0<-lapply(list(data), as.function(statistic))
  res<-lapply(data0, as.function(statistic))
  t0<-unlist(res0)
  t<-unlist(res)
  mu=mean(t)
  b=mu-t0
  s=sd(t)
  out<-matrix(c(t0,b,s),nrow = 1,dimnames = list("values",c("original","bias","std.error")))
  t=matrix(t)
  return(list(t0=t0,t=t,bootunif.Statistics=out))
}
```

The code comparing _bootunif_ to bootstrap is as follows:
```{r,eval=FALSE}
library(boot)
x<-rnorm(19,2,3)
y<-bootunif(x,mean,1000)
meanx<-function(x,i){
  x<-x[i]
  mean(x)
}
z<-boot(x,meanx,1000)
y$bootunif.Statistics
z
```

## Gauss kernel estimate(KDE) with  _fh.hat_ and _CVh_

The function of KDE _fh.hat_ is as follows:
```{r}
fh.hat<-function(x,h,data){
  if(!is.numeric(data))
    stop("data must be a numeric vector!\n")
  if(!(is.atomic(data)||is.list(data)))
    stop("data must be a numeric vector!\n")
  f<-sapply(1:length(x), function(i)(1/h)*mean(dnorm((x[i]-data)/h)))
  return(f)
}
```

The function _CVh_ to choose appropriate bandwith is as follows:
```{r}
CVh<-function(h,x){
  if(!(length(h)==2))
    stop("h must be a vector with length 2 as initial intervals!")
  if(!is.numeric(x))
    stop("data must be a numeric vector!\n")
  if(!(is.atomic(x)||is.list(x)))
    stop("data must be a numeric vector!\n")
  hs<-seq(h[1],h[2],by=0.1)
  wid=0.1
  cv<-sapply(hs,function(h){
    e<-sapply(1:length(x), function(i){
      (x[i]-fh.hat(x[i],h,x[-i]))^2
    })
    mean(e)
  })
  n<-length(hs)
  pos<-which.min(cv)
  while((pos==1)||(pos==n)||(wid>0.005)){
    hs<-seq(hs[pos]-wid,hs[pos]+wid,by=wid/10)
    if(!((pos==1)||(pos==n)))wid=wid/10
    n<-length(hs)
    cv<-sapply(hs,function(h){
      e<-sapply(1:length(x), function(i){
        (x[i]-fh.hat(x[i],h,x[-i]))^2
      })
      mean(e)
    })
    pos<-which.min(cv)
  }
  v<-hs[pos]
  return(v)
}
```

An example using above functions for KDE is as follows:
```{r}
y<-sample(0:1,size=1000,replace=TRUE,prob = c(0.7,0.3))
data<-y*rnorm(1000,0,1)+(1-y)*rnorm(1000,1,0.3)
h<-c(0.005,0.25)
CVh(h,data)
```


## _gibbs_C_ 

The code for C++ function _gibbs_C_ is as follows:
```{r,eval=FALSE}
NumericMatrix gibbs_C(int N){
  NumericMatrix mat(N, 2);
  int x0=5;
  double y0=0.5;
  int n=9;
  int a=2;
  int b=3;
  for (int i=0; i<N;i++) {
    int x = rbinom(1, n, y0)[0];
    mat(i,0)=x;
    x0=x;
    double y = rbeta(1, x0+a, n-x0+b)[0];
    mat(i,1)=y;
    y0=y;
  }
  return(mat);
}
```













